Figure 3 normalization

### 2019-05-17 main_figures/figure3_normalization.Rmd
included norm based on stable genes

```{r}
res <- readRDS("../../resNew/norm_intermediateSummary.rds")
```

@@

res.n <- readRDS("../../resNew/norm_endSummary.rds")
res.n <- res.n[which(res.n$norm != "norm.edgeR"),]
res.n$norm <- relevel(factor(res.n$norm), "norm.seurat")
levels(res.n$norm) <- gsub("norm.","",levels(res.n$norm),fixed=T)

>>>>

```{r}
res <- readRDS("../../resNew/norm2_intermediateSummary.rds")
```

@@

res.n <- readRDS("../../resNew/norm2_endSummary.rds")
res.n <- res.n[which(res.n$norm != "norm.edgeR"),]
res.n$norm <- relevel(factor(res.n$norm), "norm.seurat")
levels(res.n$norm) <- gsub("norm.","",levels(res.n$norm),fixed=T)
